\chapter{Reference Tables} \label{appendix:reference}

\section{Classic \ReplicaGenOne{} Command Reference}

The classic Replica firmware shares most commands with \ReplicaNextShort{}.
Commands 31--33 (colour control) are only active on \ReplicaNextShort{} units; other commands apply equally to both generations.

\begin{table}[htbp]
    \centering
    \caption{Primary configuration commands for classic \ReplicaGenOne{} dashboards.}
    \label{tbl:replica-commands}
    {\scriptsize
    \begin{tblr}{
        colspec = {Q[c,0.12\linewidth,cmd=\seqsplit,font=\ttfamily] Q[l,0.32\linewidth,cmd=\seqsplit] Q[l,0.52\linewidth]},
        rowsep = 2pt,
    }
        \toprule
        \SetCell{cmd=\relax}\textbf{Command} & \SetCell{cmd=\relax}\textbf{Name} & \textbf{Description} \\
        \midrule
        22 (or 0) & PARAMETER\_RPMCOEFFICIENT & Engine RPM calibration factor. \\
        1  & PARAMETER\_SPEEDCOEFFICIENT & Speed calibration factor. \\
        2  & PARAMETER\_COOLANTTHERMISTORB & Coolant thermistor beta coefficient. \\
        3  & PARAMETER\_OILTHERMISTORB & Oil thermistor beta coefficient. \\
        4  & PARAMETER\_AIRTHERMISTORB & Ambient thermistor beta coefficient. \\
        5  & PARAMETER\_TANKMINRESISTANCE & Minimum fuel sender resistance. \\
        6  & PARAMETER\_TANKMAXRESISTANCE & Maximum fuel sender resistance. \\
        7--10 & PARAMETER\_TAU\_\textit{X} & Filtering constants for coolant, oil, air, and fuel level.
        \\
        11 & PARAMETER\_MILEAGE & Total odometer value. \\
        12 & PARAMETER\_DAILY\_MILEAGE & Trip odometer. \\
        13 & PARAMETER\_AUTO\_BRIGHTNESS & Automatic brightness enable. \\
        14 & PARAMETER\_BRIGHTNESS\_LEVEL & Manual brightness level. \\
        15 & PARAMETER\_TANK\_CAPACITY & Fuel tank capacity. \\
        16 & PARAMETER\_MFA\_STATE & Active MFA mode. \\
        17 & PARAMETER\_BUZZER\_OFF & Disable buzzer (Replica only). \\
        18 & PARAMETER\_MAX\_RPM & Tachometer scaling (7000 default). \\
        19--21 & PARAMETER\_NORMAL\_RESISTANCE\_\textit{X} & Sensor resistances at \SI{25}{\celsius} for coolant, oil, and ambient inputs. \\
        23 & PARAMETER\_DOT\_OFF & Clock colon behaviour. \\
        24 & PARAMETER\_BACKLIGHT\_ON & Enable backlight when low beam is active. \\
        25 & PARAMETER\_M\_D\_FILTER & Median filter constant. \\
        26 & PARAMETER\_COOLANT\_MAX\_R & Coolant sensor threshold for full-scale indication. \\
        27 & PARAMETER\_COOLANT\_MIN\_R & Coolant sensor threshold for ``1~bar'' indication. \\
        31--33 & PARAMETER\_MAINCOLOR\_[RGB] & UI colour components (\ReplicaNextShort{} only). \\
        37 & PARAMETER\_RPM\_FILTER & RPM filtering aggressiveness. \\
        128 & PARAMETER\_READ\_ADDITION & Add 128 to read the current value of a command. \\
        255 & PARAMETER\_SET\_HOUR & Set clock hours. \\
        254 & PARAMETER\_SET\_MINUTE & Set clock minutes. \\
        253 & PARAMETER\_RESET\_DAILY\_MILEAGE & Reset trip odometer. \\
        252 & PARAMETER\_RESET\_DIGITAL & Factory reset of stored parameters. \\
        \bottomrule
    \end{tblr}}
\end{table}

\section{Classic \ReplicaGenOneShort{} Default Values}

\begin{table}[htbp]
    \centering
    \caption{Default configuration for the classic \ReplicaGenOne{}.}
    \label{tbl:replica-defaults}
    {\scriptsize
    \begin{tblr}{
        colspec = {Q[c,0.22\linewidth,cmd=\seqsplit,font=\ttfamily] Q[c,0.16\linewidth] Q[l,0.46\linewidth]},
        rowsep = 2pt,
    }
        \toprule
        \SetCell{cmd=\relax}\textbf{Parameter} & \SetCell{cmd=\relax}\textbf{Default} & \textbf{Notes} \\
        \midrule
        PARAMETER\_RPMCOEFFICIENT & 3000 &  \\
        PARAMETER\_SPEEDCOEFFICIENT & 100 &  \\
        PARAMETER\_COOLANTTHERMISTORB & 4000 &  \\
        PARAMETER\_OILTHERMISTORB & 4000 &  \\
        PARAMETER\_AIRTHERMISTORB & 3812 & 3600 on Gen~2. \\
        PARAMETER\_TANKMINRESISTANCE & 35 & Ohms. \\
        PARAMETER\_TANKMAXRESISTANCE & 265 & Ohms. \\
        PARAMETER\_TAU\_COOLANT & 2 &  \\
        PARAMETER\_TAU\_OIL & 2 &  \\
        PARAMETER\_TAU\_AIR & 2 &  \\
        PARAMETER\_TAU\_TANK & 2 &  \\
        PARAMETER\_MILEAGE & Vehicle-specific & Preserve existing odometer. \\
        PARAMETER\_DAILY\_MILEAGE & 0 &  \\
        PARAMETER\_AUTO\_BRIGHTNESS & 1 & Enabled. \\
        PARAMETER\_BRIGHTNESS\_LEVEL & 7 or 13 & Typical values for Gen~1/1.5. \\
        PARAMETER\_TANK\_CAPACITY & 63 & Litres. \\
        PARAMETER\_MFA\_STATE & 0 &  \\
        PARAMETER\_BUZZER\_OFF & 1 & Buzzer disabled. \\
        PARAMETER\_MAX\_RPM & 8000 & 7000 on earlier clusters. \\
        PARAMETER\_NORMAL\_RESISTANCE\_COOLANT & 1000 & \si{\ohm} at \SI{25}{\celsius}. \\
        PARAMETER\_NORMAL\_RESISTANCE\_OIL & 1000 & \si{\ohm} at \SI{25}{\celsius}. \\
        PARAMETER\_NORMAL\_RESISTANCE\_AMB & 2991 & \si{\ohm} at \SI{25}{\celsius}. \\
        PARAMETER\_DOT\_OFF & 0 & Blinking colon. \\
        PARAMETER\_BACKLIGHT\_ON & 1 & Enabled. \\
        PARAMETER\_M\_D\_FILTER & 65535 &  \\
        PARAMETER\_COOLANT\_MAX\_R & 120 & \si{\celsius}. \\
        PARAMETER\_COOLANT\_MIN\_R & 60 & \si{\celsius}. \\
        PARAMETER\_MAINCOLOR\_[RGB] & -- & Colour commands not active on classic Replica. \\
        PARAMETER\_RPM\_FILTER & 70 &  \\
        PARAMETER\_UPTIME & 0 &  \\
        \bottomrule
    \end{tblr}}
\end{table}

\chapter{\ReplicaNextShort{} Parameter Catalogue}\label{appendix:next-parameters}

\begin{longtblr}[
    caption={\ReplicaNextShort{} firmware parameters available through the \emph{Settings} tab.},
    label={tbl:next-parameters},
]{
    colspec = {Q[l,0.22\linewidth] Q[l,0.32\linewidth] Q[c,0.09\linewidth] Q[c,0.12\linewidth] Q[l,0.23\linewidth]},
    rowhead = 1,
    rowsep = 2pt,
}
    \toprule
    \textbf{UI label} & \textbf{Description} & \textbf{Type} & \textbf{Default} & \textbf{Range / notes} \\
    \midrule
    \SetCell[c=5]{l}{\textbf{Regional options and diagnostic toggles}} \\
    MFA Option Enable & Enable MFA steering column switch integration. & \texttt{U8} & 1 & Boolean toggle (0--1). \\
    Miles option & Display mileage in miles instead of kilometres. & \texttt{U8} & 0 & Boolean toggle (0--1). \\
    Gallons option & Show fuel consumption in gallons. & \texttt{U8} & 0 & Boolean toggle (0--1). \\
    Fahrenheit option & Display temperatures in degrees Fahrenheit. & \texttt{U8} & 0 & Boolean toggle (0--1). \\
    Kelvin option & Display temperatures in degrees Kelvin. & \texttt{U8} & 0 & Boolean toggle (0--1). \\
    Reserved option & Reserved flag for future units. & \texttt{U8} & 0 & Boolean toggle (0--1); no user-facing function. \\
    Linear fuel calculation & Calculate fuel level with a linear curve instead of table lookup. & \texttt{U8} & 0 & Boolean toggle (0--1). \\
    Test mode & Enable firmware test mode. & \texttt{U8} & 0 & Boolean toggle (0--1). \\
    \midrule
    \SetCell[c=5]{l}{\textbf{Tachometer and drivetrain}} \\
    Redline segments & Number of red warning segments on the tachometer scale. & \texttt{U8} & 8 & 0--31 segments. \\
    Diesel option & Use diesel-specific tachometer scaling. & \texttt{U8} & 0 & Boolean toggle (0--1). \\
    7k option & Switch to a \SI{7000}{rpm} tachometer scale. & \texttt{U8} & 0 & Boolean toggle (0--1). \\
    RPM Coefficient & Tachometer calibration coefficient. & \texttt{U16} & 3000 & Typical range 1000--6000. \\
    Maximum RPM & Maximum displayed RPM. & \texttt{U16} & 8000 & Selectable 6000, 7000, or 8000. \\
    RPM LPF coeff. & Low-pass filter coefficient applied while RPM increases. & \texttt{U16} & 70 & Higher values respond faster. \\
    RPM LPF coeff. fall & Low-pass filter coefficient applied while RPM decreases. & \texttt{U16} & 200 & Higher values respond faster. \\
    Stable RPM input & Optimise RPM input for modern ECUs. & \texttt{U8} & 0 & Boolean toggle (0--1). \\
    Gear change indicator & Blink the gear indicator on detected shifts. & \texttt{U8} & 1 & Boolean toggle (0--1). \\
    Rear gear coefficient & Ratio of vehicle speed to reverse gear input frequency. & \texttt{U32} & 9999999 & Sentinel value indicates not configured. \\
    1-st gear coefficient & Ratio of vehicle speed to first gear input frequency. & \texttt{U32} & 1000 & Increase to lower the detected gear. \\
    2-nd gear coefficient & Ratio of vehicle speed to second gear input frequency. & \texttt{U32} & 2000 & Increase to lower the detected gear. \\
    3-rd gear coefficient & Ratio of vehicle speed to third gear input frequency. & \texttt{U32} & 3000 & Increase to lower the detected gear. \\
    4-th gear coefficient & Ratio of vehicle speed to fourth gear input frequency. & \texttt{U32} & 4000 & Increase to lower the detected gear. \\
    5-th gear coefficient & Ratio of vehicle speed to fifth gear input frequency. & \texttt{U32} & 5000 & Increase to lower the detected gear. \\
    6-th gear coefficient & Ratio of vehicle speed to sixth gear input frequency. & \texttt{U32} & 10000 & Default indicates ``no gear''. \\
    \midrule
    \SetCell[c=5]{l}{\textbf{Temperature and fuel gauges}} \\
    Red segments count & Number of red warning segments on the temperature gauge. & \texttt{U8} & 0 & 0--3 segments. \\
    Indicate temp. sensor & Indicate a connected temperature sensor using one segment. & \texttt{U8} & 0 & Boolean toggle (0--1). \\
    Lower atten. enable & Enable the lower attenuator for the oil channel. & \texttt{U8} & 0 & Boolean toggle (0--1). \\
    Temp. alarm function & Flash the temperature gauge when an alarm triggers. & \texttt{U8} & 0 & Boolean toggle (0--1). \\
    Min. coolant temp. & Minimum coolant temperature shown as a single segment. & \texttt{U16} & 60 & Expressed in \si{\celsius}. \\
    Max. coolant temp. & Coolant temperature mapped to a full-scale reading. & \texttt{U16} & 120 & Expressed in \si{\celsius}. \\
    Coolant LPF coeff. & Low-pass filter constant for coolant readings. & \texttt{U16} & 2 & Higher values respond faster. \\
    Oil LPF coeff. & Low-pass filter constant for oil readings. & \texttt{U16} & 2 & Higher values respond faster. \\
    Air LPF coeff. & Low-pass filter constant for ambient readings. & \texttt{U16} & 2 & Higher values respond faster. \\
    Tank LPF coeff. & Low-pass filter constant for fuel level readings. & \texttt{U16} & 2 & Higher values respond faster. \\
    Fuel tank min. resistance & Minimum resistance of the fuel level sender. & \texttt{U16} & 35 & Expressed in \ohm. \\
    Fuel tank max. resistance & Maximum resistance of the fuel level sender. & \texttt{U16} & 265 & Expressed in \ohm. \\
    Fuel tank capacity & Fuel tank capacity. & \texttt{U8} & 63 & Expressed in litres. \\
    \midrule
    \SetCell[c=5]{l}{\textbf{Signal processing and measurement}} \\
    Other blink & Use dedicated left/right indicator inputs instead of the common wire. & \texttt{U8} & 0 & Boolean toggle (0--1). \\
    Touch sensor option & Enable the wireless touch sensor input. & \texttt{U8} & 0 & Boolean toggle (0--1). \\
    Invert light signal input & Invert the headlight brightness trigger input. & \texttt{U8} & 0 & Boolean toggle (0--1). \\
    Consumption sensor option & Enable the external consumption MAF sensor. & \texttt{U8} & 0 & Boolean toggle (0--1). \\
    Indicator filter cycles & Cycles required to confirm indicator changes. & \texttt{U16} & 0 & 0--65535 cycles. \\
    Turn signal filter cycles & Cycles required to confirm turn signal changes. & \texttt{U16} & 0 & 0--65535 cycles. \\
    Speedometer measurement period in ms & Pulse counter integration period. & \texttt{U32} & 1000 & Adjustable 250--2000~ms. \\
    Speedometer measurement window in ms & Averaging window for the speed pulse counter. & \texttt{U32} & 1000 & Adjustable 250--2000~ms. \\
    Stable Speed input & Optimise the speed input for electronic vehicle speed sensors. & \texttt{U8} & 0 & Boolean toggle (0--1). \\
    Filtered Speed input & Enable software filtering of the speed input. & \texttt{U8} & 1 & Boolean toggle (0--1). \\
    LPF coefficient for speed calculation & Low-pass filter constant for speed calculations. & \texttt{U16} & -- & Default depends on firmware build. \\
    Median filter threshold & Legacy display filter threshold. & \texttt{U16} & 65535 & Reserved for diagnostics. \\
    \midrule
    \SetCell[c=5]{l}{\textbf{Sensor calibration constants}} \\
    Speed coefficient & Speedometer calibration factor. & \texttt{U16} & 100 & Increase to raise the indicated speed. \\
    Coolant thermistor beta & Beta coefficient for the coolant temperature sensor curve. & \texttt{U16} & 4000 & Typical range 3000--4500. \\
    Oil thermistor beta & Beta coefficient for the oil temperature sensor curve. & \texttt{U16} & 4000 & Typical range 3000--4500. \\
    Air thermistor beta & Beta coefficient for the ambient temperature sensor curve. & \texttt{U16} & 3812 & Generation~2 panels use \num{3812}. \\
    Coolant default resistance & Coolant sensor resistance at \SI{25}{\celsius}. & \texttt{U16} & 1000 & Expressed in \ohm. \\
    Oil default resistance & Oil sensor resistance at \SI{25}{\celsius}. & \texttt{U16} & 1000 & Expressed in \ohm. \\
    Air default resistance & Ambient sensor resistance at \SI{25}{\celsius}. & \texttt{U16} & 2991 & Expressed in \ohm. \\
    Coolant pull-up & Pull-up resistor used for the coolant sensor. & \texttt{U16} & 220 & Expressed in \ohm. \\
    Oil pull-up & Pull-up resistor used for the oil sensor. & \texttt{U16} & 3300 & Expressed in \ohm. \\
    Amb. air pull-up & Pull-up resistor used for the ambient sensor. & \texttt{U16} & 3300 & Expressed in \ohm. \\
    \midrule
    \SetCell[c=5]{l}{\textbf{Display, brightness, and audio}} \\
    Auto brightness & Enable automatic display brightness control. & \texttt{U8} & 1 & Boolean toggle (0--1). \\
    Brightness level & Manual brightness level. & \texttt{U8} & 25 & Adjustable 0--70. \\
    Light signal min & ADC reading that maps to minimum brightness. & \texttt{U16} & 300 & Raw ADC units. \\
    Light signal max & ADC reading that maps to maximum brightness. & \texttt{U16} & 800 & Raw ADC units. \\
    Brightness min & Minimum automatic brightness level. & \texttt{U8} & 6 & Display intensity units. \\
    Brightness max & Maximum automatic brightness level. & \texttt{U8} & 25 & Display intensity units. \\
    Brightness speed & Percentage applied per adjustment step. & \texttt{U8} & 10 & Adjustable 0--100\%. \\
    Buzzer option & Enable or disable the integrated buzzer. & \texttt{U8} & 1 & 1 disables, 0 enables. \\
    Blinking dot & Control the colon animation on the clock. & \texttt{U8} & -- & 0 blinks, 1 holds steady. \\
    Bkclt power & Enable the backlight power rail. & \texttt{U8} & 1 & Boolean toggle (0--1). \\
    Main R color & Red component of the main theme. & \texttt{U8} & 180 & RGB value (0--255). \\
    Main G color & Green component of the main theme. & \texttt{U8} & 240 & RGB value (0--255). \\
    Main B color & Blue component of the main theme. & \texttt{U8} & 6 & RGB value (0--255). \\
    Back R color & Red component of the backlight. & \texttt{U8} & 180 & RGB value (0--255). \\
    Back G color & Green component of the backlight. & \texttt{U8} & 240 & RGB value (0--255). \\
    Back B color & Blue component of the backlight. & \texttt{U8} & 6 & RGB value (0--255). \\
    Custom scheme & Enable loading of a custom colour scheme. & \texttt{U8} & 0 & Boolean toggle (0--1). \\
    WiFi Auto Off & Automatically disable Wi-Fi after one minute of ignition on. & \texttt{U8} & 0 & Boolean toggle (0--1). \\
    \midrule
    \SetCell[c=5]{l}{\textbf{Runtime values}} \\
    MFA function state & Current MFA page index. & \texttt{U8} & -- & Runtime value (not stored). \\
    MFA Block ind. & Selected MFA memory block. & \texttt{U8} & -- & Runtime value (not stored). \\
\bottomrule
\end{longtblr}

\chapter{Document Change Log} \label{app:change-log}

\begin{table}[htbp]
    \centering
    \caption{Document change registration sheet.}
    \label{tbl:change-log}
    {\scriptsize
    \begin{tblr}{
        colspec = {Q[c,0.12\linewidth] Q[l] Q[c,0.2\linewidth]},
        rowsep = 2pt,
    }
        \toprule
        \textbf{Change} & \textbf{Affected sheets} & \textbf{Date} \\
        \midrule
        1 & 04.10.2022 & 04~Oct~2022 \\
        2 & 31.08.2023 & 31~Aug~2023 \\
        3 & 05.08.2024 & 05~Aug~2024 \\
        4 & LaTeX document introduced. & 22.09.2025 \\
        \bottomrule
    \end{tblr}}
\end{table}
