\setcounter{chapter}{13}
\chapter{Product Coding and Supply Variants} \label{ch:notation}
\markboth{Product Coding and Supply Variants}{Product Coding and Supply Variants}

Digifiz Replica dashboards are identified by a four-letter code that captures drivetrain support, assembly method, speed sensor type, and wiring generation.
Optional suffixes indicate the maximum supported engine speed and the units shown on the display.
Understanding these codes is essential when matching the instrument cluster to a specific vehicle harness.

\section{Model Coding Scheme}

\begin{description}
    \item[First letter] \textbf{G} indicates petrol engines, while \textbf{D} identifies diesel variants.
    \item[Second letter] \textbf{A} denotes a factory-assembled dashboard and \textbf{M} denotes a kit for self-assembly.
    \item[Third letter] \textbf{C} means the cluster expects a mechanical cable speed sensor; \textbf{R} selects the remote electronic speed sensor.
    \item[Fourth letter] \textbf{T} is compatible with the pre-facelift (CE~1) wiring loom; \textbf{S} targets the facelift (CE~2) harness.
\end{description}

An optional trailing digit marks the maximum engine speed displayed on the tachometer (for example, the ``8'' in \texttt{GACT8} maps to an 8000~rpm scale).
Export-oriented instrument panels append a unit designator: \texttt{M} for miles per hour, \texttt{G} for gallons, \texttt{F} for Fahrenheit, and \texttt{K} for Kelvin.
Thus, \texttt{GART8-MGF} identifies a petrol panel with a remote speed sensor, CE~1 harness, 8000~rpm tachometer, and imperial units.

\section{Model Range}

\begin{tblr}{
        colspec = {>{\ttfamily}Q[l,0.25\linewidth] Q[l]},
        row{1} = {font=\bfseries},
        rowsep = 3pt,
    }
    \toprule
    Model & Description \\
    \midrule
    GACT    & Petrol, fully assembled, cable speed sensor, dual connectors, 7000~rpm scale. \\
    GART    & Petrol, fully assembled, electronic speed sensor, dual connectors, 7000~rpm scale. \\
    GAC     & Petrol, fully assembled, cable speed sensor, single connector, 7000~rpm scale. \\
    GARS    & Petrol, fully assembled, electronic speed sensor, single connector, 7000~rpm scale. \\
    GACT8   & Petrol, cable speed sensor, dual connectors, 8000~rpm scale. \\
    GART8   & Petrol, electronic speed sensor, dual connectors, 8000~rpm scale. \\
    GACS8   & Petrol, cable speed sensor, single connector, 8000~rpm scale. \\
    GARS8   & Petrol, electronic speed sensor, single connector, 8000~rpm scale. \\
    DACT    & Diesel, cable speed sensor, dual connectors, 6000~rpm scale. \\
    DART    & Diesel, electronic speed sensor, dual connectors, 6000~rpm scale. \\
    DACS    & Diesel, cable speed sensor, single connector, 6000~rpm scale. \\
    DARS    & Diesel, electronic speed sensor, single connector, 6000~rpm scale. \\
    MT      & Self-assembly kit with dual connectors. \\
    MS      & Self-assembly kit with a single connector. \\
    NEXT-GART & Replica Next, dual connectors, electronic speed sensor, 8000~rpm scale. \\
    NEXT-GARS & Replica Next, single connector, electronic speed sensor, 8000~rpm scale. \\
    NEXT-MT & Replica Next self-assembly kit with dual connectors. \\
    NEXT-MS & Replica Next self-assembly kit with a single connector. \\
    \bottomrule
\end{tblr}

\section{Supplied Components}

Each dashboard ships with the parts required for its configuration:
\begin{itemize}
    \item A Digifiz Replica harness includes the assembled dashboard, a dual-channel temperature harness (ambient and oil), a USBasp programmer, and a speed sensor harness with sensor for remote-drive variants.
    \item A Digifiz Replica Next kit includes the dashboard and the electronic speed sensor harness with sensor; the Wi-Fi configuration interface replaces the USB programmer.
\end{itemize}

Additional packaging recommendations and transport rules are provided in \Cref{ch:Summary}.
