\chapter{Typical situations for setting up the \ReplicaGenOne{}}\label{ch:replica-scenarios}

Before troubleshooting, confirm that the dashboard is the classic \ReplicaGenOne{} (\autoref{ch:replica-setup}). \ReplicaNextLong{} panels use a Wi-Fi portal and are covered in \autoref{ch:replica-next-scenarios}.

\begin{description}
    \item[Bluetooth module not detected] Pair with the dashboard's Bluetooth Classic interface (it normally advertises as \texttt{Digifiz}). Serial Bluetooth Terminal for Android remains the recommended tool: configure the end-of-line character as LF and avoid BLE-only scanners, which cannot discover the module.
    \item[iPhone or iPad cannot connect] \ReplicaGenOneShort{} dashboards use Bluetooth~2.0 and are incompatible with iOS devices. Use an Android phone or a computer running a Bluetooth serial utility.
    \item[Commands ignored on 2024+ firmware] Unlock the command parser by sending \InlineCode{234 123}, then repeat the desired sequence. Store quick-access buttons in Serial Bluetooth Terminal for the values you adjust frequently.
    \item[Speed reading too high or low] Connect through Serial Bluetooth Terminal, drive at an indicated \SI{100}{\kilo\metre\per\hour}, and note the GPS speed. Send command \InlineCode{1} with the measured speed (for example, \InlineCode{1 85}) so \texttt{PARAMETER\_SPEEDCOEFFICIENT} matches the verified GPS value.
    \item[RPM reading incorrect] Firmware prior to 2024 expects command \InlineCode{0} followed by the value, while current releases use \InlineCode{22}. Audi engines typically need \InlineCode{22 3000}; halve or double the value (for example, \InlineCode{22 1500} or \InlineCode{22 6000}) until the display matches the tachometer.
    \item[Increase brightness] Disable automatic control with \InlineCode{13 0} and raise the manual level with command \InlineCode{14} (for example, \InlineCode{14 50}). Values between 45 and 55 brighten the display substantially; avoid levels above 60 to preserve LED life. Re-enable the photodiode later with \InlineCode{13 1}.
    \item[Setting the clock] Use Serial Bluetooth Terminal to send command \InlineCode{255} with the desired hour and then \InlineCode{254} with the minutes. Examples: \InlineCode{255 23} and \InlineCode{254 55} set 23:55; \InlineCode{255 14} and \InlineCode{254 30} set 14:30; \InlineCode{255 2} and \InlineCode{254 28} set 02:28.
    \item[Fuel gauge issues] Disconnect the vehicle battery before probing.\begin{itemize}
        \item If the display drifts from 60 to 0, measure the sender resistance between the harness pin and ground; valid readings are typically \SIrange{30}{300}{\ohm}. Clean the connector and confirm the signal reaches the main board.
        \item If the gauge is pegged full, look for a short to ground below \SI{5}{\ohm} on the sender line and repair it.
        \item If the reading never changes, compare the sender resistance with full and empty tanks. Replace the sensor if it stays constant.
    \end{itemize}
    \item[Fuel flow values seem wrong] The flow channel is emulated unless an intake-manifold pressure sensor is fitted. Treat the reading as indicative rather than absolute.
    \item[Coolant gauge inaccurate] Adjust \texttt{PARAMETER\_COOLANT\_MIN\_R} and \texttt{PARAMETER\_COOLANT\_MAX\_R}. Example: \InlineCode{27 30} shortens the scale so that the ``1~bar'' mark aligns with roughly \SI{30}{\celsius}.
    \item[Oil or ambient temperature readings missing] A reading of \texttt{-999} or a stuck value indicates a sensor issue. With the battery disconnected and the engine cold, measure the sensor resistance between the harness pin and ground. Oil sensors should read about \SI{2}{\kilo\ohm} \ensuremath{\pm}\SI{0.3}{\kilo\ohm}; ambient sensors about \SI{10}{\kilo\ohm} \ensuremath{\pm}\SI{2}{\kilo\ohm}. Adjust \texttt{PARAMETER\_NORMAL\_RESISTANCE\_OIL} (command~20) or \texttt{PARAMETER\_NORMAL\_RESISTANCE\_AMB} (command~21) if the display needs fine-tuning. Persistent faults should be documented with \InlineCode{adc 0} logs and escalated to PHOL-LABS Kft support.
\end{description}

Collect raw sensor data with \InlineCode{adc 0} if the problem persists and share the results with the dashboard developers for analysis.
